\thispagestyle{plain}
\newpage
\chaptermark{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{Acknowledgements}
\begin{center} \large\bf {ACKNOWLEDGEMENTS}
\end{center}
\vspace{1cm}  
Foremost, I would like to express my sincere gratitude to my advisor Prof. Dr. Binil Aryal for the continuous support of my study and research, for his patience, motivation, enthusiasm, and immense knowledge. His guidance helped me all the time of research and writing of this dissertation. I could not have imagined a better advisor and mentor for my dissertation.
\\
\\
My sincere thanks goes to  Dr.
Ho Seong Hwang of Department of Physics and Astronomy, Seoul
National University, Korea, for providing data base of rotating clusters.\\\\
I acknowledge to Prof. W. Saurer (Innsbruck University, Austria) and Mr. Rajesh Kumar Bachchan (Lund Observatory)
for providing support during the work.
\\\\
I would like to offer my sincere gratitude to Prof. Dr. Lok Narayan Jha,
Head of Central Department of Physics. My sincere
thanks also goes to Central Library, all professors, teachers and
whole staffs of Central Department of Physics for their direct or
indirect support in my work.
\\
\\
It is impossible to list here the name of all my friends who helped, encouraged and adviced during the work.
However, I would be delighted to extend gratefulness to my
colleagues Mr. Ishowr Poudel, Mr. Ramesh Pandey, Mr. Saroj Dhakal and Mr. Saroj Dangi and all my friends who helped me
directly and indirectly for this work.
\\
\\
My special thanks goes to my  brother Mr. Shishir Bhattarai, my sister Ms. Sushmita Pandey and  my parents
for their constant support and encouragemet during the work.
\\
\\
\vspace{0.001cm}\\

